 Group Report

### 2024-12-10 draft.Rmd
Update draft.Rmd

From this model, we got an $R^2$ value of 0.259, meaning that our model 
explains 25.9% of the variance in log of (G1_G2_Average). Additionally, 
this $R^2$ value did not improve, and the $R^2$ value our model achieve 
is not that high indicating that the relationship between target and 
predictor might not have a log-linear relationship between them.

@@

The summary of our model shows that all four variables are statistically
significant at a critical value of 0.05, indicating to us that these
four variables have a meaningful relationship with G1_G2_Average.
Specifically, \* schoolMS has a negative correlation with
log(G1_G2_Average) with estimate -1.42. This implies that being in
school MS (Mousinho da Silveira) as compared to school GP (Gabriel
Pereira) is associated with a decrease in log(G1_G2_Average) by 1.42
when other variables are constant \* Medu has a positive correlation of
0.215, implying that for a unit increase in Mother's educational level,
the log(G1_G2_Average) increases by 0.215 units. \* higherYes has a
positive correlation of 2.41, implying that an increase in 2.41 units in
log(G1_G2_Average) is observed for students planning to pursue a degree
compared to those who are not interested. \* absences has a negative
correlation of 0.131, implying that every additional day of absences is
associated with a decrease in log(G1_G2_Average) by 0.131 units.

@@

In conclusion, although our model provides statistical significant
results for all four predictors, the low $R^2$ value of 0.259 suggests
that there might be other predictor variables influencing
log(G1_G2_Average) that are not captured in our analysis. Further
exploration and analysis of the predictor variables in the future may
help with defining these relationships.

>>>>

From this model, we got an $R^2$ value of 0.294, meaning that our model 
explains 29.4% of the variance in log of (G1_G2_Average). Additionally, 
this $R^2$ value did improve from our regular model by 0.0169. However,
the $R^2$ value our model achieve is not that high indicating that 
the relationship between target and predictor might not have a 
log-linear relationship between them.

@@

The summary of our model shows that all four variables are statistically
significant at a critical value of 0.05, indicating to us that these
four variables have a meaningful relationship with G1_G2_Average.
Specifically, \* schoolMS has a negative correlation with
log(G1_G2_Average) with estimate -0.18. This implies that being in
school MS (Mousinho da Silveira) as compared to school GP (Gabriel
Pereira) is associated with a decrease in log(G1_G2_Average) by 0.18
when other variables are constant \* Medu has a positive correlation of
0.0242, implying that for a unit increase in Mother's educational level,
the log(G1_G2_Average) increases by 0.0242 units. \* higherYes has a
positive correlation of 0.172, implying that an increase in 0.172 units in
log(G1_G2_Average) is observed for students planning to pursue a degree
compared to those who are not interested. \* absences has a negative
correlation of 0.00665, implying that every additional day of absences is
associated with a decrease in log(G1_G2_Average) by 0.00665 units.

@@

In conclusion, although our model provides statistical significant
results for all four predictors, the low $R^2$ value of 0.294 suggests
that there might be other predictor variables influencing
log(G1_G2_Average) that are not captured in our analysis. Further
exploration and analysis of the predictor variables in the future may
help with defining these relationships.
